Factor Analysis on Citations, Using a Combined Latent and Logistic Regression Model

### 2019-10-08 Manuscript for submission/manuscript.tex
Update

%Astute readers might notice the slight difference of the first term in objective function between (\ref{eq:logistic10}) and (\ref{eq:Modified}).
For the convenience of theoretical investigation, we slightly modify the first term in the objective function summing over all $(i,j)$ pairs.
After scaling, due to symmetry of $X$,$L$, and $S$, the only difference between (\ref{eq:logistic10}) and (\ref{eq:Modified}) is in the inclusion of terms in diagonal pairs $(i,i),\forall i=1,\dots,n$.
%the first term in the objective function in (\ref{eq:Modified}) sums over all $(i,j)$ pairs.
This slight modification leads to neither theoretical consequence nor noticeable difference in practice.
Let ($\widehat{\alpha},\widehat{L},\widehat{S}$) be the solution to (\ref{eq:Modified}), and ($\alpha^{*},L^{*},S^{*}$) be the ground truth, which governs the data generating process.
Let $\widehat{\Theta}$ and $\Theta^{*}$ be defined respectively as $\widehat{\Theta} = \widehat{\alpha}\mathbbm{1}\mathbbm{1}^T+\widehat{L}+\widehat{S}$ and $\Theta^{*} = \alpha^{*}\mathbbm{1}\mathbbm{1}^T+L^{*}+S^{*}$.
And denote the error term for each parameter as $\widehat{\Delta}^{\Theta} = \widehat{\Theta}-\Theta^{*},
\widehat{\Delta}^{\alpha} = \widehat{\alpha}-\alpha^{*},
\widehat{\Delta}^L = \widehat{L}-L^{*},
\widehat{\Delta}^S = \widehat{S}-S^{*}.$
Throughout the discussion, let $P^{*}=\bigg\{\frac{\exp(\Theta_{ij}^{*})}{1+\exp(\Theta_{ij}^{*})}\bigg\}_{1 \leq i,j \leq n} \in \mathbb{R}^{n \times n}$.
We then impose several assumptions for theoretical guarantees of our estimator.

@@

%\begin{landscape}
\begin{table}[htbp]
\centering
\begin{tabular}{clcl}\hline
Pair & Community & Title (Author, Year) & \\
\hline
1    & FuncAn    & Properties of principal component methods for functional and longitudinal data analysis (P. Hall, et al. $2006$)      & \\
     & VarSel    & Nonconcave penalized likelihood with a diverging number of parameters (J. Fan, et al, $2004$)                       & \\
2    & VarSel      & The adaptive lasso and its oracle properties (H. Zou, $2006$)                             & \\
     & Mixed    & Nonparametric Bayes conditional distribution modeling with variable selection (Y. Chung, et al. $2009$)    & \\
3    & DimRed    & Contour projected dimension reduction (R. Luo, et al. $2009$)                                                     & \\
     & VarSel    & Factor profiled sure independence screening (H. Wang, $2012$)& \\
4    & VarSel    & Factor profiled sure independence screening (H. Wang, $2012$)& \\
     & DimRed    & Sliced regression for dimension reduction (H. Wang, et al. $2012$) & \\
5    & CovEst    & Two sample tests for high-dimensional covariance matrices (J. Li, et al. $2012$)& \\
     & VarSel      & The sparsity and bias of the {LASSO} selection in high-dimensional linear regression (CH. Zhang, et al. $2008$)        & \\
6    & MulT    & Innovated higher criticism for detecting sparse signals in correlated noise (P. Hall, et al. $2010$)       & \\
     & CovEst     & Regularized estimation of large covariance matrices (PJ. Bickel, et al. $2008$)    &  \\
7    & DimRed    & A constructive approach to the estimation of dimension reduction directions (Y. Xia. $2007$)       & \\
     & VarSel     & Factor profiled sure independence screening (H. Wang, $2012$)    & \\
8    & VarSel    & A majorization-minimization approach to variable selection using spike and slab priors (TJ. Yen, $2011$) & \\
     & Mixed      & Empirical {B}ayes selection of wavelet thresholds (IM. Johnstone, et al. $2005$)                         & \\
9    & Mixed    & Nonparametric inferences for additive models (J. Fan, et al. $2005$)                  & \\
     & VarSel    & Nonparametric independence screening in sparse ultra-high-dimensional additive models
     (J. Fan, et al. $2011$)     & \\
10   & VarSel    & Sure independence screening in generalized linear models with {NP}-dimensionality
    (J. Fan, et al. $2010$) & \\
     & Mixed     & Maximum likelihood estimation in semi-parametric regression models with censored data (D. Zeng, et al. $2007$) & \\
\hline
\end{tabular}
\caption{Top $10$ edges come from pairs of papers from different communities. For instance in the first pair, $\emph{FuncAn}$ paper cites $\emph{VarSel}$ paper for borrowing a mathematical representation to build a theorem. But they are not related in terms of topic.}
\end{table}
\label{tab:table2}
%\end{landscape}

>>>>

%Astute readers might notice the slight difference of the first term in objective function between (\ref{eq:logistic10}) and (\ref{eq:Modified}).
For the convenience of theoretical investigation, we slightly modify the first term in the objective function summing over all $(i,j)$ pairs.
After scaling, due to symmetry of $X$,$L$, and $S$, the only difference between (\ref{eq:logistic10}) and (\ref{eq:Modified}) is in the inclusion of terms in diagonal pairs $(i,i),\forall i=1,\dots,n$.
%the first term in the objective function in (\ref{eq:Modified}) sums over all $(i,j)$ pairs.
We borrow the idea of this modification from the work of \cite{ma2017exploration}, where they also consider the latent factor model in analyzing the embedded topics in the network but without the sparse component.
As stated in \cite{ma2017exploration}, this slight modification leads to neither theoretical consequence nor noticeable difference in practice.
Let ($\widehat{\alpha},\widehat{L},\widehat{S}$) be the solution to (\ref{eq:Modified}), and ($\alpha^{*},L^{*},S^{*}$) be the ground truth, which governs the data generating process.
Let $\widehat{\Theta}$ and $\Theta^{*}$ be defined respectively as $\widehat{\Theta} = \widehat{\alpha}\mathbbm{1}\mathbbm{1}^T+\widehat{L}+\widehat{S}$ and $\Theta^{*} = \alpha^{*}\mathbbm{1}\mathbbm{1}^T+L^{*}+S^{*}$.
And denote the error term for each parameter as $\widehat{\Delta}^{\Theta} = \widehat{\Theta}-\Theta^{*},
\widehat{\Delta}^{\alpha} = \widehat{\alpha}-\alpha^{*},
\widehat{\Delta}^L = \widehat{L}-L^{*},
\widehat{\Delta}^S = \widehat{S}-S^{*}.$
Throughout the discussion, let $P^{*}=\bigg\{\frac{\exp(\Theta_{ij}^{*})}{1+\exp(\Theta_{ij}^{*})}\bigg\}_{1 \leq i,j \leq n} \in \mathbb{R}^{n \times n}$.
We then impose several assumptions for theoretical guarantees of our estimator.

@@

%\begin{landscape}
\begin{table}[htbp]
\centering
\begin{tabular}{clcl}\hline
Pair & Community & Title  & \\
\hline
1    & FuncAn    & Properties of principal component methods for functional and longitudinal data analysis       & \\
     & VarSel    & Nonconcave penalized likelihood with a diverging number of parameters                        & \\
2    & VarSel      & The adaptive lasso and its oracle properties                              & \\
     & Mixed    & Nonparametric Bayes conditional distribution modeling with variable selection     & \\
3    & DimRed    & Contour projected dimension reduction                                                      & \\
     & VarSel    & Factor profiled sure independence screening & \\
4    & VarSel    & Factor profiled sure independence screening & \\
     & DimRed    & Sliced regression for dimension reduction  & \\
5    & CovEst    & Two sample tests for high-dimensional covariance matrices & \\
     & VarSel      & The sparsity and bias of the {LASSO} selection in high-dimensional linear regression         & \\
6    & MulT    & Innovated higher criticism for detecting sparse signals in correlated noise      & \\
     & CovEst     & Regularized estimation of large covariance matrices   &  \\
7    & DimRed    & A constructive approach to the estimation of dimension reduction directions       & \\
     & VarSel     & Factor profiled sure independence screening   & \\
8    & VarSel    & A majorization-minimization approach to variable selection using spike and slab priors & \\
     & Mixed      & Empirical {B}ayes selection of wavelet thresholds               & \\
9    & Mixed    & Nonparametric inferences for additive models          & \\
     & VarSel    & Nonparametric independence screening in sparse ultra-high-dimensional additive model  & \\
10   & VarSel    & Sure independence screening in generalized linear models with {NP}-dimensionality & \\
     & Mixed     & Maximum likelihood estimation in semi-parametric regression models with censored data & \\
\hline \\
\end{tabular}

\begin{tabular}{ccccc}
\hline
Pair $1$                                                                                 & Pair $2$                                                                       & Pair $3$                                                                             & Pair $4$                                                                            & Pair $5$                                                                              \\ \hline
\begin{tabular}[c]{@{}c@{}}P. Hall, et al. $2006$\\ J. Fan, et al. $2004$\end{tabular}     & \begin{tabular}[c]{@{}c@{}}H. Zou. $2006$\\ Y. Chung, et al. $2009$\end{tabular} & \begin{tabular}[c]{@{}c@{}}R. Luo, et al. $2009$\\ H. Wang. $2012$\end{tabular}        & \begin{tabular}[c]{@{}c@{}}H. Wang. $2012$\\ H. Wang, et al. $2012$\end{tabular}      & \begin{tabular}[c]{@{}c@{}}J. Li, et al. $2012$\\ CH. Zhang, et al. $2008$\end{tabular} \\ \hline
Pair $6$                                                                                 & Pair $7$                                                                       & Pair $8$                                                                             & Pair $9$                                                                            & Pair $10$                                                                             \\ \hline
\begin{tabular}[c]{@{}c@{}}P. Hall, et al. $2010$\\ PJ. Bickel, et al. $2008$\end{tabular} & \begin{tabular}[c]{@{}c@{}}Y. Xia. $2007$\\ H. Wang. $2012$\end{tabular}         & \begin{tabular}[c]{@{}c@{}}TJ. Yen. $2011$\\ IM. Johnstone, et al. $2005$\end{tabular} & \begin{tabular}[c]{@{}c@{}}J. Fan, et al. $2005$\\ J. Fan, et al. $2011$\end{tabular} & \begin{tabular}[c]{@{}c@{}}J. Fan, et al. $2010$\\ D. Zeng, et al. $2007$\end{tabular}
\\ \hline
\end{tabular}
\caption{Top $10$ edges come from pairs of papers from different communities.
Authors and years of publication for the papers in each pair are also presented.
In the first pair, $\emph{FuncAn}$ paper cites $\emph{VarSel}$ paper for borrowing a mathematical representation to build a theorem. 
But they are not related in terms of topic.}
\label{tab:table2}
%\end{landscape}
\end{table}
